\chapter{Introduction} \label{i}

This chapter introduces the topics and motivation for the project overall. The main goals will be discussed in section \ref{i--project-goals} followed by an outline of the chapters in this report.

\section{Project Goals} \label{i--project-goals}

The main goal of this project is to create a progressive web application (PWA). Progressive web applications are looking to take the best of the web and of native application development. Specifically some of the aspects of progressive web applications to be explored in the project are: Progressive enhancement of features and connectivity independent. \cite{pwa}

Secondary goals including the research, experimentation and implementation of principles such as Performance as User Experience, offline first and modern web technologies such as Service Workers, Virtual DOM and clientside databases.

\section{Report Outline} \label{i--report-outline}

The rest of this report is organised as follows:

Chapter \ref{l-r} reviews home-brewing and user experience through performance. Home-brewing is explained and compared to software. This is followed by an in depth discussion of user experience through performance, including techniques and methodologies to achieve performance.

Chapter \ref{a-d} describes the design of the proposed solution. Topics in the section include: Discussion of tooling, design methodologies, sourcing and usage of data and choice of technologies. The requirements for the implementation are defined here.

Chapter \ref{s-i} describes the system implementation of the proposed solution and testing. Based on the design this section discusses the implementation and interesting problems found.

Chapter \ref{t-e} describes the testing and evaluation. The section includes description of the testing set-up, the results from testing and how well the requirements were fulfilled with examples. Other overall evaluation is given here reflecting on the project as a whole.

Chapter \ref{c} is the conclusion with future work. Here the report is wrapped up with some final thoughts.
